Liveness-Based Garbage Collection for Lazy Languages

### 2015-07-10 paper/paper.tex
Updated

While exploring the heap, the GC  may encounter closures. In RGC mode,
the  closure will  be  explored as  usual and  copied  by passing  the
references. Since our liveness analysis  predicts the liveness of data
in its evaluated form only, closures  present a challenge for LGC. LGC
will need  to map the  liveness of the  free variables of  the closure
back  to their  evaluation point.  This  situation can  be handled  in
multiple ways and hence we present 2 algorithms for handling closures.

@@

        \caption{LGC with closure collection based on liveness.\label{algo:lgc-a}}
\end{algorithm}
Algorithm~\ref{algo:lgc-a}  describes  a  liveness-based  garbage  collection
scheme.   The algorithm  assumes that  checking for  liveness involves
traversing the  liveness-DFAs stored as  a table and does  not mention
this explicitly.  Starting  with the root set, each  live reference is
explored   using  $\mathit{  lgcCopy}$.    Copying  \CONS\   cells  is
simple---it  just involves  copying  the cell  itself and  recursively
copying the \CAR\ and  the \CDR\ fields.  Liveness-based collection of
closures  is more  complicated since  our analysis  only  computes the
liveness of evaluated objects and not closures.

>>>>

While exploring the heap, the GC  may encounter closures. In RGC mode,
the closure  will be explored  as usual  and copied by  traversing the
references corresponding to the arguments. Since our liveness analysis
predicts the  liveness of  data in its  evaluated form  only, closures
present a challenge for LGC. LGC will  need to map the liveness of the
free variables of the closure to  their evaluation point.  This is not
straight  forward as  variables may  escape their  creation scope  and
needs to  be handled in an  approximate way.  We describe this in detail next.

@@

        \caption{LGC with closure collection based on liveness.\label{algo:lgc-a}}
\end{algorithm}
Algorithm~\ref{algo:lgc-a}  describes  a  liveness-based  garbage  collection
scheme.    Starting  with the root set, each  live reference is
explored   using  $\mathit{  lgcCopy}$.    Copying  \CONS\   cells  is
simple---it  just involves  copying  the cell  itself and  recursively
copying the \CAR\ and  the \CDR\ fields.
